---
title: "Data Import"
output: github_document
---

```{r}
library(tidyverse)
library(readxl)
library(haven)
```

Let's import a dataset

```{r}
litters_df = 
  read_csv("data_import_examples/FAS_litters.csv")
```

look at your data!

```{r}
names(litters_df)
```

Update the names in 'litters_df'.

```{r}
litters_df = 
  janitor::clean_names(litters_df)
```

Look at the data!!!

```{r}
litters_df
```

Sometimes skimming data is neat?

```{r}
skimr::skim(litters_df)
```

## Fix the missingness

```{r}
litters_df =
  read_csv("data_import_examples/FAS_litters.csv", na = c("NA", ".", ""))
```

## Import new dataset (FAS_pups)

```{r}
pups = 
  read_csv("data_import_examples/FAS_pups.csv")
```

```{r}
pups_df=
  read_csv(
    "data_import_examples/FAS_pups.csv",
    skip = 3,
    na = c("NA", ".", "")
  )

pups_df = 
  janitor::clean_names(pups_df)

pups_df
```

## What about excel

CSVs are really great but sometimes you get an excel file.

```{r}
mlb_df = 
  read_excel("data_import_examples/mlb11.xlsx")
```

Import LotR word counts.

```{r}
fotr_df=
  read_excel("data_import_examples/LotR_Words.xlsx", range = "B3:D6")
```

## Importing data from SAS

Import the PULSE dataset

```{r}
pulse_df =
  read_sas("data_import_examples/public_pulse_data.sas7bdat")

pulse_df = 
  janitor::clean_names(pulse_df)
```

## Why does Jeff hate read.csv so much?

```{r}
litters_df_base = 
  read.csv("data_import_examples/FAS_litters.csv")
```

```{r, eval = FASLE}
litters_df_base = 
  read.csv("data_import_examples/FAS_litters.csv")
```

## What about data exporting?

```{r}
write_csv(fotr_df, "data_import_examples/fotr_df.csv")
```


















  
